---
title: "Data Quality Check Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: yes
    theme: united 
params:
  adv1: NA
  adv2: NA
  adv3: NA
  adv4: NA
  sca1: NA
  sca2: NA
  sca3: NA
  hds1: NA
  hds2: NA
  hds3: NA
  rcs1: NA
  rcs2: NA
  rcs3: NA
  hhs1: NA
  hhs2: NA
  hhs3: NA
  lcs1: NA
  lcs2: NA
  lcs3: NA
  fcsdayplot: NA
  rcsidayplot: NA
    
---

```{r, echo=FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=7, error=FALSE, warning=FALSE, message=FALSE) 

# Function to safely render plots
safe_plot <- function(plot_obj, title = "Plot not available") {
  if(is.null(plot_obj)) {
    cat(paste("**", title, "**: Data not available or variables missing\n\n"))
  } else {
    tryCatch({
      plot_obj
    }, error = function(e) {
      cat(paste("**", title, "**: Error generating plot -", e$message, "\n\n"))
    })
  }
}
```


## Submission
### Result by Admin1
```{r, echo=FALSE}
safe_plot(params$adv1, "Submission by Admin1")
```

### Result by Admin2

```{r, echo=FALSE}
safe_plot(params$adv2, "Submission by Admin2")
```

### Result by Enumerator
```{r, echo=FALSE}
safe_plot(params$adv3, "Submission by Enumerator")
```
### Result by Enumerator by admin2

```{r, echo=FALSE}
safe_plot(params$adv4, "Submission by Enumerator by Admin2")
```


## Food Consumption Score (FCS)
### Result by Admin1

```{r, echo=FALSE}
safe_plot(params$sca1, "FCS by Admin1")
```

### Result by Admin2
```{r, echo=FALSE}
safe_plot(params$sca2, "FCS by Admin2")
```

### Result by Enumerator

```{r, echo=FALSE}
safe_plot(params$sca3, "FCS by Enumerator")
```

### Day-by-Day FCS Analysis

```{r, echo=FALSE}
safe_plot(params$fcsdayplot, "FCS Day-by-Day Analysis")
```
## Household Dietary Diversity Score (HDDS)
### Result by Admin1

```{r, echo=FALSE}
safe_plot(params$hds1, "HDDS by Admin1")
```
### Result by Admin2

```{r, echo=FALSE}
safe_plot(params$hds2, "HDDS by Admin2")
```
### Result by Enumerator

```{r, echo=FALSE}
safe_plot(params$hds3, "HDDS by Enumerator")
```
## Reduced Copying Strategy Index (rCSI)
### Result by Admin1

```{r, echo=FALSE}
safe_plot(params$rcs1, "rCSI by Admin1")
```
### Result by Admin2

```{r, echo=FALSE}
safe_plot(params$rcs2, "rCSI by Admin2")
```

### Result by Enumerator
```{r, echo=FALSE}
safe_plot(params$rcs3, "rCSI by Enumerator")
```

### Day-by-Day rCSI Analysis

```{r, echo=FALSE}
safe_plot(params$rcsidayplot, "rCSI Day-by-Day Analysis")
```

## Household Hunger Scale (HHS)
### Result by Admin1
```{r, echo=FALSE}
safe_plot(params$hhs1, "HHS by Admin1")
```
### Résultat Admin2
```{r, echo=FALSE}
safe_plot(params$hhs2, "HHS by Admin2")
```
### Result by Enumerator
```{r, echo=FALSE}
safe_plot(params$hhs3, "HHS by Enumerator")
```
## Livelihood Coping Strategy Index (LCS)
### Result by Admin1
```{r, echo=FALSE}
safe_plot(params$lcs1, "LCS by Admin1")
```
### Result by Admin2
```{r, echo=FALSE}
safe_plot(params$lcs2, "LCS by Admin2")
```
### Result by Enumerator

```{r, echo=FALSE}
safe_plot(params$lcs3, "LCS by Enumerator")
